---
title: "DGI db Tutorial"
author: "Jenny Smith"
date: "September 10, 2019"
output: html_document
---

#Set-up 

```{r setup}
library(knitr)
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=50),tidy=TRUE, 
                      fig.align='center', fig.width = 10, fig.height = 10)
knitr::opts_knit$set(root.dir =
                       file.path(PROJHOME,"2018.08.29_CBL_Exon8-9_Deletions/AAML1031/"))
options(stringsAsFactors = FALSE)

```

```{r message = FALSE, warning=FALSE}
library(stringr)
library(magrittr)
library(ggplot2)
library(dplyr)
library(tidyr)
library(tibble)
library(readr)
library(DeGSEA)
getwd()
```


#Gene list

```{r}
ADCs <- read.csv(file.path(PROJHOME,"0000.00.02_Reference_GeneInfo/Full_ADC_Target_Database_rmDuplicates_08.28.2019.csv"), row.names = 1)

# head(ADCs)
```


#rDGIdb 
https://bioconductor.org/packages/release/bioc/html/rDGIdb.html


```{r}
# BiocManager::install("rDGIdb")
library(rDGIdb)
```

```{r}
genes <- ADCs$Gene.symbol.of.ADC.target..Cleaned.
```

With a vector of genes, we can query DGIdb using the queryDGIdb() function. The argument
genes is a required argument, all other arguments are optional. These optional arguments
are used as filters. If they are not provided, the query returns all results for a specific gene.

```{r}
result <- queryDGIdb(genes)
```


The results are available in the following four formats:

-Result summary Drug-gene interactions summarized by the source(s) that reported them.

-Detailed results Search terms matching exactly one gene that has one or more drug interactions.

-By gene Drug interaction count and druggable categories associated with each gene.

-Search term summary Summary of the attempt to map gene names supplied by the user
to gene records in DGIdb.

```{r}
## Result summary
resultSummary(result) %>% head()
```

```{r}
## Detailed results
detailedResults(result) %>% 
  arrange(Gene) %>%
  head(n=10)
```

```{r}
## By gene
byGene(result) %>% head()
```

```{r}
## Search term summary
searchTermSummary(result) %>% head()
```


#Filters 

Druggable genome: https://www.ncbi.nlm.nih.gov/pubmed/28356508
DGI: https://academic.oup.com/nar/article/46/D1/D1068/4634012

```{r}
resultFilter <- queryDGIdb(genes, 
                           geneCategories = c("CLINICALLY ACTIONABLE"))

```

```{r}
finalRes <- detailedResults(resultFilter)  

dim(finalRes)
tail(finalRes)
```

```{r}
deDupRes <- detailedResults(resultFilter) %>% 
  group_by(Gene) %>% 
  mutate_at(vars(Drug:PMIDs), ~collapseRows(col = ., uniq = FALSE, sep="; ")) %>% 
  ungroup()  %>%
  unique()


dim(finalRes)
```

```{r}
head(finalRes)

table(duplicated(finalRes$Gene))
```

