---
title: "Concatenate RNA-seq"
author: "Jenny Smith"
date: "June 6, 2019"
output: html_document
---
  
  
```{r setup}
library(knitr)
knitr::opts_knit$set(root.dir = file.path(PROJHOME))
```

```{r}
knitr::opts_chunk$set(tidy.opts=list(width.cutoff=50),tidy=TRUE,
                      fig.align='center', fig.height = 5, fig.width = 5)
options(stringsAsFactors = FALSE)
```

```{r message=FALSE}
library(dplyr)
library(ggplot2)
library(stringr)
library(reshape2)
getwd()
```

```{r}
source("~/scripts/conversion_scripts/Merge_Cat_FixDupIDs_Function.r")
source("~/scripts/RNAseq_Analysis/DifferentialExpn_PathwayAnalysis/R/rmDupGenes_Function.r")
```




#Define Functions to be used. 

```{r}
#Function for the TPM conversion. 
# Based on https://groups.google.com/forum/#!topic/rsem-users/W9RQrZIOzA4
#Useage: sapply(cated$RPKM, RPKM_to_TPM)

RPKM_to_TPM <- function(RPKM){
  conversionFactor <- sum(RPKM) / 1E6
  TPM <- RPKM / conversionFactor
  return(TPM)
}
```


```{r}
#https://stackoverflow.com/questions/32040742/dplyrselect-including-all-other-columns-at-end-of-new-data-frame-or-beginni

addCols <- function(df,symbol){
  library(dplyr)
  
  df <- df %>%
    as.data.frame() %>%
    mutate(geneSymbol=symbol) %>%
    select(geneSymbol, everything())
  
  return(df)
}
```

#Download Files from S3

```{bash}
ml awscli 
cd /fh/scratch/delete90/meshinchi_s/jlsmith3/kallisto/SWOG
BUCKET="s3://fh-pi-meshinchi-s"
aws s3 cp --only-show-errors --recursive  --exclude "*" --include "*.h5" --include "*.json"  $BUCKET/SR/SWOG/kallisto_out/ .
```



#Identify Files to Be Concatenated


```{r}
filepath <-  ""

allfiles <- paste0(filepath, dir(path = filepath, 
                                 pattern = ""))

head(allfiles)
```


```{r}
length(allfiles) #6 AML files 
```



#Columns Description


#Begin Concatenation 


```{r}
#Pattern to select the Target Barcode
pattern <- "^.+\\/([BPR][A-Z0-9].+R)\\_.+"

```

```{r}
#Select the column indices 
selected <- c(1,2)
```

```{r results='hide'}
cated <- catExpnData(filenames = allfiles,regex =  pattern, cols = selected, header = FALSE)
names(cated) <- c("geneSymbol","Counts")
```

```{r}
lapply(cated, head)

lapply(cated,dim)
```



#Check that the Gene Ids are in the Same Order


```{r}
apply(cated$geneSymbol,2, function(x) identical(x=x,y=cated$geneSymbol[,1]))
```

#Add in TPMs

#Add in TPMs 

```{r}
cated[["TPM"]] <- apply(cated$RPKM,2, RPKM_to_TPM)

table(apply(cated[["TPM"]], 2, sum)) #all sum to 1 million 
```


#Add columns for the Gene Symbol and Ensembl Symbol 


```{r}
withCols <- addCols(df=cated$Counts, symbol = cated$geneSymbol[,1])

head(withCols)
# lapply(withCols, function(x) lapply(x, function(i) head(i[,1:5])))
```


#Save the output

```{r}
# write.csv(withCols, "TARGET_AML_1031_DS.AML_HTSeq_Counts.csv", row.names = FALSE)
```



NOTE:
  
  If markdown cannot be completed with pandoc (memory issues), use the following

> library("rmarkdown")
> render("~/scripts/RNAseq_Analysis/DifferentialExpn_PathwayAnalysis/TARGET_AML_1031_Cat_RNAseq.Rmd", "html_document")


#Session Info

```{r}
sessionInfo()
```

